Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-06-27 2016-Weak-FH-Bisim/WeakBisim.tex
both directions for lemma 5

\begin{proof} 
($\Rightarrow$) First, we prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
Suppose that $\Pred_{s,t}\in \mathcal{R}$ 
%and for any open transition $OT$ in $\mathcal{T}_1$:
% \begin{mathpar}
%     \openrule
%         {
%           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
%         {s \OTarrow {\alpha} s'}
%\end{mathpar}
%there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
% \begin{mathpar}
%    \openrule
%         {
%           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
%         {t \OTWeakarrow {\alpha_x} t_x}
%\end{mathpar}
% such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
% and  \\
% $\Pred_{s,t} \land \Pred_{OT}\\
% \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
%   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
%     \land \alpha\!=\!\alpha_x\land  
%     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
and  suppose that the following statement holds:
\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'} \in \WT_1

@@

\TODO{we miss the other direction no?}

>>>>

\begin{proof} Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definition, namely: \\
($\Rightarrow$) We prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
suppose that $\Pred_{s,t}\in \mathcal{R}$ 
%and for any open transition $OT$ in $\mathcal{T}_1$:
% \begin{mathpar}
%     \openrule
%         {
%           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
%         {s \OTarrow {\alpha} s'}
%\end{mathpar}
%there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
% \begin{mathpar}
%    \openrule
%         {
%           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
%         {t \OTWeakarrow {\alpha_x} t_x}
%\end{mathpar}
% such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
% and  \\
% $\Pred_{s,t} \land \Pred_{OT}\\
% \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
%   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
%     \land \alpha\!=\!\alpha_x\land  
%     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
and  suppose that the following statement holds:
\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'} \in \WT_1

@@
